---
title: "parsing multiple XML records"
output: html_notebook
---

```{r}
library(XML)
library(tidyverse)
```

```{r}
xml2 <- xmlParse("./biosample_result-4.xml")
xmltop2 = xmlRoot(xml2)
NumRecords = xmlSize(xmltop2)
```

How many antibiogram records for each sample?
Vector of row lengths for each sample
```{r}
# rows_per_record <- sapply(1:1000, function(x) xpathSApply(xmltop2,paste0('//*[',x,']/Description/Comment/Table/Body/Row/Cell'),xmlValue))
# # check that number of records = number of tables
# assertthat::assert_that(NumRecords == length(rows_per_record))
# 
# headers_per_record <- sapply(1:1000, function(x) xpathSApply(xmltop2, paste0('//*[',x,']/Description/Comment/Table/Header/Cell'), xmlValue))
# assertthat::assert_that(NumRecords == length(rows_per_record))
```

Get all the IDs and make a row for every record of every strain.  
```{r}
# BioSampleIDs <- sapply(1:NumRecords, function(x) xmlValue(xmltop2[[x]][['Ids']][[1]]))
# #commenting out the SRAIDS becasue it turns out that you cant guarantee that it is elelment 3 of 'Ids' and can be matched using other queries
# #SRAIDs <- sapply(1:NumRecords, function(x) xmlValue(xmltop2[[x]][['Ids']][[3]]))
# Organisms <- sapply(1:NumRecords, function(x) xmlValue(xmltop2[[x]][['Description']][['Organism']]))
# #T_head_uniq <- unique(headers_per_record)[[1]]

```

Function to populate rows for each sample
```{r}
populate_rows <- function(k){
  # k is the record ID from the larger table named  xmltop2
  T_vals <- xpathSApply(xmltop2,paste0('//*[',k,']/Description/Comment/Table/Body/Row/Cell'),xmlValue)
  T_cols <- xpathSApply(xmltop2, paste0('//*[',k,']/Description/Comment/Table/Header/Cell'), xmlValue)
  numcols <- length(T_cols)
  numrows <- length(T_vals)/numcols
  df <- data.frame(BioSample = rep(xmlValue(xmltop2[[k]][['Ids']][[1]]),numrows),Organism = rep(xmlValue(xmltop2[[k]][['Description']][['Organism']]),numrows))   
  # add all the columns
  df[T_cols] <- NA
  #loop to ad each row (faster structure?)
  for (x in 1:numrows) {
  vs = 1+(x-1)*numcols
  ve = 1+(x-1)*numcols+(numcols-1)
  df[x,3:(numcols+2)]=T_vals[vs:ve]
  }
return(df)
}
```

Turns out some BioSample records have different numbers of tables
```{r}
all_comments <- sapply(1:NumRecords, function(x) xmlSize(xmltop2[[x]][['Description']][['Comment']]))
table(all_comments)
```
Filter out those with multiple comments (==multiple tables)
```{r}
samples_to_process <- which(all_comments == 1)
```


```{r}
combined_df <- map_df(samples_to_process,populate_rows,.progress = TRUE)
```

```{r}
write_tsv(combined_df,"./ncbi_antibiograms_20230312.tsv")
```

To Do - investigate all_comments > 1
Fixed problems with SRA and Organism

731 S. aureus genomes with drug info
```{r}
combined_df %>%
  filter(grepl("aureus",Organism)) %>%
  group_by(BioSample) %>%
  summarize()
```

